Neural and Symbolic Spatiotemporal Optimization of Cosmological Particle-Mesh Simulation

### 2023-03-05 docs/papers/sto/sto.tex
FIXUP draft: add xxx acknowledgement
FIXUP draft: typo

\title[Spatiotemporally Optimized Simulation]
{Neural and Symbolic Spatiotemporal Optimization of Cosmological
Particel-Mesh Simulation}

@@

The Flatiron Institute is supported by the Simons Foundation.

>>>>

\title[Spatiotemporally Optimized Simulation]
{Neural and Symbolic Spatiotemporal Optimization of Cosmological
Particle-Mesh Simulation}

@@

YZ and YL were supported by The Major Key Project of PCL.
The Flatiron Institute is supported by the Simons Foundation.
